%%%% One-Page Resume (Data Analyst) %%%%

\documentclass[letterpaper,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{CormorantGaramond}
\usepackage{charter}
\usepackage{xcolor}

\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.85in}
\addtolength{\textheight}{1.65in}

\setlength{\multicolsep}{-3pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\raggedbottom
\raggedright

\input{glyphtounicode}
\pdfgentounicode=1

%---------- Custom Commands ----------%

\newcommand{\documentTitle}[2]{
  \begin{center}
    {\Huge\color{accentTitle} #1}\\[6pt]
    {\color{accentLine}\hrule}\vspace{2pt}
    {\footnotesize #2}\par\vspace{2pt}
    {\color{accentLine}\hrule}
  \end{center}
}

\titleformat{\section}{
  \vspace{-6pt}\color{accentText}\raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

\newenvironment{resume_list}{
  \vspace{-4pt}
  \begin{itemize}[leftmargin=18pt, itemsep=-3pt]
}{
  \end{itemize}
}

\renewcommand\labelitemi{--}

%---------- Document ----------%

\begin{document}

\documentTitle{Krushna Shinde}{
  \href{tel:+919022710360}{\faPhone\ +91 9022710360} ~|~
  \href{mailto:krushnashinde1012@gmail.com}{\faEnvelope\ krushnashinde1012@gmail.com} ~|~
  \href{https://www.linkedin.com/in/krushna-shinde-549165276/}{\faLinkedin\ linkedin.com/in/krushna-shinde} ~|~
  \href{https://github.com/Krishna101211}{\faGithub\ github.com/Krushnashinde}
}

%---------------------------%
% Summary
%---------------------------%

\section*{Summary}
Detail-oriented Data Analyst with strong expertise in SQL, Python, and Power BI. Experienced in data cleaning, transformation, exploratory data analysis (EDA), and dashboard development. Skilled at deriving actionable business insights from large datasets to support data-driven decision-making. Microsoft PL-300 certified with hands-on experience in end-to-end analytics projects.

%---------------------------%
% Skills
%---------------------------%

\section*{Skills}
\begin{tabular}{p{0.32\linewidth} p{0.65\linewidth}}
  \textbf{Programming:} & Python (oops,file handling, exception handling),pandas, numpy \\
  \textbf{Data Analysis:} & Data Cleaning, Data Visualization\\
  \textbf{BI Tools:} & Power BI, Microsoft Excel \\
  \textbf{Databases:} & SQL, Joins, Subqueries \\
  \textbf{Tools:} & Jupyter Notebook, Google Colab, VS Code, GitHub \\
  \textbf{Concepts:} & ETL Process, Data Modeling, Dashboard Design \\
  \textbf{Soft Skills:} & Analytical Thinking, Problem Solving, Communication \\
\end{tabular}

%---------------------------%
% Projects
%---------------------------%

\section*{Projects}

\textbf{Customer Behavior Data Analytics (Python, SQL, Power BI)} 
\hfill \href{https://github.com/Krishna101211/Customer-behaviour-/blob/main/customer_behavior_dashboard.pdf}{Link}
\begin{resume_list}
  \item Performed end-to-end data analysis including data cleaning, transformation, and EDA using Python.
  \item Designed SQL queries to analyze revenue trends, customer demographics, and discount impact.
  \item Built an interactive Power BI dashboard to visualize KPIs such as total revenue, customer segmentation, and purchase behavior.
  \item Generated actionable insights that improved understanding of customer buying patterns.
\end{resume_list}

\textbf{IT Industry Database Analytics Project (SQL)} 
\hfill \href{https://github.com/Krishna101211/SQL-IT-DataBase}{Link}
\begin{resume_list}
  \item Designed a relational database with multiple entities including Employee, Department, Project, Client, and Performance.
  \item Wrote advanced SQL queries to answer 10+ business questions such as top-performing employees, project revenue analysis, and department-wise salary distribution.
  \item Applied constraints techniques to ensure data integrity and efficiency.
  \item Simulated real-world IT company analytics use cases.
\end{resume_list}

\textbf{Blinkit Sales Analysis Dashboard (Power BI, Excel)} 
\hfill \href{https://github.com/Krishna101211/Blinkit-sales-analysis-/blob/main/Blinkit.pdf}{Link}
\begin{resume_list}
  \item Analyzed Blinkit grocery sales dataset to identify trends in product categories, outlet performance, and customer ratings.
  \item Performed data cleaning and transformation using Power Query.
  \item Created DAX measures for KPIs such as Total Sales, Average Rating, and Outlet-wise Revenue.
  \item Designed interactive dashboard with slicers and visualizations to support business decision-making.
\end{resume_list}

%---------------------------%
% Activities
%---------------------------%

\section*{Activities}
\textbf{Microsoft Learn Student Club (MLSC)} – Design \& Media Lead \hfill May 2023 -- Dec 2023
\begin{resume_list}
  \item Collaborated with technical and non-technical teams to support event execution and technical content delivery.
  \item Designed data-driven visuals and improved communication across teams.
\end{resume_list}


%---------------------------%
% Certifications
%---------------------------%

\section*{Certifications}
\begin{resume_list}
  \item \textbf{Microsoft PL-300: Power BI Data Analyst} – Microsoft Certified (2025)
  \item Prompt Engineering – Udemy
  \item MS-CIT Certification
  \item Qspider Data analyst(python,sql,powerbi)
\end{resume_list}

%---------------------------%
% Education
%---------------------------%

\section*{Education}

\textbf{B.E. in Computer Science – GES R.H. Sapat College of Engineering, Nashik (SPPU)} \hfill 2025 \\
\textit{CGPA: 6.9} \\[-2pt]

\textbf{HSC – HPT Arts and RYK Science College} \hfill 2021 \\
\textit{81\%} \\[-2pt]

\textbf{SSC – Madhyamik Vidyalaya, Untwadi} \hfill 2019 \\
\textit{82.40\%}

\end{document}
