%%%%
% One-Page Resume – SDET Intern (Prophecy ATS Optimized)
%%%%
\documentclass[letterpaper,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{CormorantGaramond}
\usepackage{charter}
\usepackage{xcolor}

\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.8in}
\addtolength{\textheight}{1.5in}

\raggedbottom
\raggedright

\input{glyphtounicode}
\pdfgentounicode=1

\newcommand{\documentTitle}[2]{
  \begin{center}
    {\Huge\color{accentTitle} #1}\\[6pt]
    {\color{accentLine}\hrule}\vspace{2pt}
    {\footnotesize #2}\par\vspace{2pt}
    {\color{accentLine}\hrule}
  \end{center}
}

\titleformat{\section}{
  \vspace{-8pt}\color{accentText}\raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule\vspace{-6pt}]

\newenvironment{resume_list}{
  \vspace{-4pt}\begin{itemize}[itemsep=-2pt, leftmargin=18pt]
}{
  \end{itemize}
}

\renewcommand\labelitemi{--}

\begin{document}

%---------------------------%
% Header
%---------------------------%
\documentTitle{Krushna Shinde}{
  \href{tel:+919022710360}{\faPhone\ +91 9022710360} ~|~
  \href{mailto:krushnashinde1012@gmail.com}{\faEnvelope\ krushnashinde1012@gmail.com} ~|~
  \href{https://www.linkedin.com/in/krushna-shinde-549165276/}{\faLinkedin\ linkedin.com/in/krushna-shinde} ~|~
  \href{https://github.com/Krishna101211}{\faGithub\ github.com/Krishna101211}
}

%---------------------------%
% Summary
%---------------------------%
\section*{Summary}
SDET Intern aspirant with strong programming fundamentals in Python and SQL, and a solid understanding of Software Development Life Cycle (SDLC) and Agile methodologies. Hands-on experience in manual testing, data validation, debugging, and validating end-to-end software workflows through real-world projects. Comfortable writing test scenarios, collaborating with developers, and learning automation testing tools. Highly motivated to grow as a Software Development Engineer in Test in a fast-paced startup environment.

%---------------------------%
% Skills
%---------------------------%
\section*{Skills}
\begin{tabular}{p{0.32\linewidth} p{0.65\linewidth}}
\textbf{Programming:} & Python, SQL \\
\textbf{Testing Concepts:} & Manual Testing, Test Case Design, Test Scenarios, Bug Identification \\
\textbf{Automation (Learning):} & Selenium (Basics), Automation Testing Concepts \\
\textbf{Data Validation:} & Data Accuracy Checks, Exploratory Testing, Debugging \\
\textbf{Tools:} & Git, GitHub, VS Code, Jupyter Notebook, Google Colab \\
\textbf{CI/CD (Exposure):} & GitHub Actions (Basic Understanding) \\
\textbf{Methodologies:} & SDLC, Agile Development \\
\textbf{Soft Skills:} & Problem-Solving, Collaboration, Curiosity, Adaptability \\
\end{tabular}

%---------------------------%
% Projects
%---------------------------%
\section*{Projects}

\textbf{Customer Behavior Analytics System (Python, SQL, Power BI)}  
\begin{resume_list}
  \item Performed manual testing and validation of end-to-end data pipelines to ensure accuracy and reliability.
  \item Designed test scenarios to verify SQL query outputs, business logic, and transformed datasets.
  \item Debugged Python scripts to resolve data inconsistencies and improve data quality.
  \item Collaborated with stakeholders to validate dashboards against source data.
\end{resume_list}

\textbf{IT Industry Database Management System (SQL)}  
\begin{resume_list}
  \item Designed and tested a relational database system consisting of 8 normalized tables.
  \item Executed manual testing of CRUD operations, joins, constraints, and indexing.
  \item Wrote SQL validation queries to ensure data integrity and consistency.
  \item Strengthened understanding of backend systems and database testing.
\end{resume_list}

\textbf{Sales Insights Dashboard (Power BI)}  
\begin{resume_list}
  \item Conducted functional testing of dashboards to validate KPIs and calculated measures.
  \item Verified ETL logic implemented using Power Query and DAX calculations.
  \item Performed exploratory testing to identify edge cases and reporting defects.
  \item Improved reporting reliability through iterative defect resolution.
\end{resume_list}

%---------------------------%
% Testing Knowledge
%---------------------------%
\section*{Testing Knowledge}
\begin{resume_list}
  \item Understanding of Manual Testing, Defect Life Cycle, and Test Documentation.
  \item Familiar with Black Box Testing and basic Automation Testing principles.
  \item Exposure to CI/CD workflows and version control using Git.
  \item Actively learning Selenium and Python-based test automation frameworks.
\end{resume_list}

%---------------------------%
% Certifications
%---------------------------%
\section*{Certifications}
\begin{resume_list}
  \item \textbf{Microsoft Certified: PL-300 – Power BI Data Analyst Associate} (2025)
  \item 100 Days of Python Programming Bootcamp – Udemy
  \item Prompt Engineering Fundamentals – Udemy
  \item Zensar Employability Skills Development Program
  \item MS-CIT Certification
\end{resume_list}

%---------------------------%
% Activity
%---------------------------%
\section*{Leadership \& Activities}
\textbf{Microsoft Learn Student Club (MLSC)} – Design \& Media Lead \hfill May 2023 – Dec 2023  
\begin{resume_list}
  \item Collaborated with cross-functional teams to support technical and analytics-focused events.
  \item Demonstrated ownership, communication, and teamwork in a fast-paced environment.
\end{resume_list}



\end{document}
