
%%%% One-Page Resume (Data Analyst / GenAI Developer) %%%%

\documentclass[letterpaper,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{CormorantGaramond}
\usepackage{charter}
\usepackage{xcolor}

\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.85in}
\addtolength{\textheight}{1.65in}

\setlength{\multicolsep}{-3pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\raggedbottom
\raggedright

\input{glyphtounicode}
\pdfgentounicode=1

%---------- Custom Commands ----------%

\newcommand{\documentTitle}[2]{
  \begin{center}
    {\Huge\color{accentTitle} #1}\\[6pt]
    {\color{accentLine}\hrule}\vspace{2pt}
    {\footnotesize #2}\par\vspace{2pt}
    {\color{accentLine}\hrule}
  \end{center}
}

\titleformat{\section}{
  \vspace{-6pt}\color{accentText}\raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

\newenvironment{resume_list}{
  \vspace{-4pt}
  \begin{itemize}[leftmargin=18pt, itemsep=-3pt]
}{
  \end{itemize}
}

\renewcommand\labelitemi{--}

%---------- Document ----------%

\begin{document}

\documentTitle{Krushna Shinde}{
  \href{tel:+919022710360}{\faPhone\ +91 9022710360} ~|~
  \href{mailto:krushnashinde1012@gmail.com}{\faEnvelope\ krushnashinde1012@gmail.com} ~|~
  \href{https://www.linkedin.com/in/krushna-shinde-549165276/}{\faLinkedin\ linkedin.com/in/krushna-shinde} ~|~
  \href{https://github.com/Krishna101211}{\faGithub\ github.com/Krushnashinde}
}

%---------------------------%
% Summary
%---------------------------%

\section*{Summary}
Detail-oriented Data Analyst and aspiring GenAI Developer with expertise in Python, SQL, and Power BI. Experienced in building RAG-based AI systems, backend APIs using FastAPI, and performing end-to-end data analysis. Skilled in deriving actionable insights and developing scalable AI-powered applications.

%---------------------------%
% Skills
%---------------------------%

\section*{Skills}
\begin{tabular}{p{0.32\linewidth} p{0.65\linewidth}}
  \textbf{Programming:} & Python, SQL \\
  \textbf{Frameworks:} & FastAPI, LangChain, LangGraph, React \\
  \textbf{Cloud \& DevOps:} & AWS (EC2, S3, CodePipeline, CodeBuild), Docker, GitHub Actions \\
  \textbf{Databases:} & SQL, postgres\\
  \textbf{AI/ML:} & RAG, Basic Machine Learning, HuggingFace Embeddings, CrossEncoder Reranking \\
  \textbf{Data Tools:} & Power BI, Excel, Pandas, NumPy \\
  \textbf{Tools:} & Git, GitHub, Postman (API Testing), VS Code \\
\end{tabular}

%---------------------------%
% Experience
%---------------------------%

\section*{Experience}

\textbf{Data Analyst Intern – Robowave} \hfill Jan 2025 – Feb 2025
\begin{resume_list}
  \item Collected, cleaned, and analyzed datasets using SQL and Python.
  \item Built Power BI dashboards to visualize KPIs and business metrics.
  \item Generated insights to improve operational efficiency.
\end{resume_list}

\textbf{MLOps \& Backend Engineer Intern – Blocksone} \hfill Feb 2025 – Present
\begin{resume_list}
  \item Contributed to backend development using Python, working on APIs and real-world application workflows.
  \item Gained experience in product development lifecycle from initial design to deployment stages.
  \item Debugged API issues in large codebases, improving system stability and performance.
  \item Built foundational knowledge in blockchain, reinforcement learning, and collaborative development practices.
\end{resume_list}

%---------------------------%
% Projects
%---------------------------%

\section*{Projects}

\textbf{Lawyer Friend — AI Traffic Law Assistant (FastAPI, Langchain)} 
\hfill \href{https://huggingface.co/spaces/krushna101211/traffic-lawyer}{Link}
\begin{resume_list}
  \item Built a full-stack RAG-based legal assistant to answer Maharashtra traffic law queries with source citations.
  \item Designed hybrid retrieval pipeline (vector + BM25), Reciprocal Rank Fusion, and CrossEncoder reranking.
  \item Implemented a self-correcting LangGraph agent with query rephrasing and answer regeneration.
  \item Developed a structure-aware document ingestion system extracting legal metadata using regex.
  \item Integrated Redis memory, caching, and Docker-based deployment for production readiness.
\end{resume_list}

\textbf{Customer Behavior Data Analytics (Python, SQL, Power BI)} 
\hfill \href{https://github.com/Krishna101211/Customer-behaviour-/blob/main/customer_behavior_dashboard.pdf}{Link}
\begin{resume_list}
  \item Performed end-to-end data analysis including data cleaning, transformation, and EDA using Python.
  \item Designed SQL queries to analyze revenue trends, customer demographics, and discount impact.
  \item Built an interactive Power BI dashboard to visualize KPIs such as total revenue, customer segmentation, and purchase behavior.
  \item Generated actionable insights that improved understanding of customer buying patterns.
\end{resume_list}

\textbf{Blinkit Sales Analysis Dashboard (Power BI, Excel)} 
\hfill \href{https://github.com/Krishna101211/Blinkit-sales-analysis-/blob/main/Blinkit.pdf}{Link}
\begin{resume_list}
  \item Analyzed sales data to identify trends in product categories and outlet performance.
  \item Performed data cleaning and transformation using Power Query.
  \item Created DAX measures for KPIs such as Total Sales and Average Rating.
  \item Designed interactive dashboards for business decision-making.
\end{resume_list}

%---------------------------%
% Activities
%---------------------------%

\section*{Activities}
\textbf{Microsoft Learn Student Club (MLSC)} – Design \& Media Lead \hfill May 2023 -- Dec 2023
\begin{resume_list}
  \item Collaborated with teams for event execution and technical content delivery.
  \item Designed visuals to improve communication and engagement.
\end{resume_list}

%---------------------------%
% Certifications
%---------------------------%

\section*{Certifications}
\begin{resume_list}
  \item \textbf{Microsoft PL-300: Power BI Data Analyst} – Microsoft Certified (2025)
  \item Prompt Engineering – Udemy
  \item MS-CIT Certification
  \item QSpiders Data Analyst (Python, SQL, Power BI)
\end{resume_list}

%---------------------------%
% Education
%---------------------------%

\section*{Education}

\textbf{B.E. in Computer Science – GES R.H. Sapat College of Engineering, Nashik (SPPU)} \hfill 2025 \\
\textit{CGPA: 6.9} \\[-2pt]

\textbf{HSC – HPT Arts and RYK Science College} \hfill 2021 \\
\textit{81\%} \\[-2pt]

\textbf{SSC – Madhyamik Vidyalaya, Untwadi} \hfill 2019 \\
\textit{82.40\%}

\end{document}
